Methods and Results

### 2021-05-03 ms.Rmd
Small change
Added some new analyses to tackle Pau's predcitions

  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)

@@

  # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
  model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)

  model1.5_nonZ <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust_model1.5_nonZ <- robust(model1.5_nonZ, cluster = data$study)

@@

@@

As males and females of a species become more similar in size (i.e., increasing SSD index converging on 0) female fitness is more negatively impacted when increasing male harm (i.e., larger fitness decrease observed in treatmemt group or a more positive effect size) (unstandardised slope, $\beta_{SSD}$ = `r robust_model1.5_nonZ$beta[4]`, 95% CI = `r robust_model1.5_nonZ$ci.lb[4]` to `r robust_model1.5_nonZ$ci.ub[4]`,  $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation; Figure \@ref(fig:SSD)). However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`). Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any concrete conclusions premature.

@@

# References

>>>>

  # Marginalised Harmtype        
  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)

@@

  # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
  model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = data)

  model1.5_inter <- rma.mv(SMDH ~  Harm_type + zSSD + Harm_type:zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = data)

  # Does SSD effect vary by harm type. No evidence for interaction
   aicc_ssd_interact <- AICc(model1.5, model1.5_inter)
  dAICc_ssd_interact <- max(aicc_ssd_interact$AICc) - min(aicc_ssd_interact$AICc)

  # Update models with REML now
        model1.5 <- update(model1.5, method = "REML" )

  # Non Z transform
  model1.5_nonZ <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust_model1.5_nonZ <- robust(model1.5_nonZ, cluster = data$study)

@@

  # Sperm competition intensity. Use ML because comparing fixed effects. 
  sperm_data <- data %>% filter(!SCR.SCI == "hermaphrodite" & !is.na(zSSD))

  model1.7_inetr <- rma.mv(SMDH ~  SCR.SCI*zSSD, V = sperm_data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = sperm_data)

  model1.7 <- rma.mv(SMDH ~  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = sperm_data)

  # Check for interaction
   # Compare AICc for each model
    aicc_1.7 <- AICc(model1.7_inetr, model1.7)
  d_aicc_1.7 <- max(aicc_1.7$AICc) - min(aicc_1.7$AICc) # Main effect model better supported

  # Robust
         model1.7 <- update(model1.7, method = "REML")
  robust_model1.7 <- robust(model1.7, cluster = sperm_data$study, vcov = "CR2")

  model1.7_reparam <- rma.mv(SMDH ~ 0 +  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "REML", data = sperm_data)
  robust_model1.7_reparam <- robust(model1.7_reparam, cluster = sperm_data$study, vcov = "CR2")

  # Tables
                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)

@@

As males and females of a species become more similar in size (i.e., increasing SSD index converging on 0) female fitness is more negatively impacted when increasing male harm (i.e., larger fitness decrease observed in treatmemt group or a more positive effect size) (unstandardised slope, $\beta_{SSD}$ = `r robust_model1.5_nonZ$beta[4]`, 95% CI = `r robust_model1.5_nonZ$ci.lb[4]` to `r robust_model1.5_nonZ$ci.ub[4]`,  $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation; Figure \@ref(fig:SSD)). However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`). In addition, there was no evidence that the effect of SSD varied according to the type of male harm exhibited (i.e., no interaction between Harm Type and SSD; $\Delta_{AIC_{c}}$ =`r dAICc_ssd_interact`, with the main effects model having the lowest $AIC_{c}$). Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any concrete conclusions premature.

@@

#### Sperm competition intensity

Species with higher sperm intensity had a tendeny to have significantly larger effect sizes overall (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`; Figure \@ref(fig:sperm)).

```{r sperm, fig.width = 7.625, fig.height = 6.750, fig.cap="Species sperm competition intensity and the effect of changes in male harm on female fitness. }

sperm_data <- data %>% filter(!SCR.SCI == "hermaphrodite")

contrast_sperm <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.7$beta[2], digit = 2))

contrast_sperm2 <- paste0("95% CI:", round(robust_model1.7$ci.lb[2], digit = 2), " to ", round(robust_model1.7$ci.ub[2], digit = 2))

contrast_sperm3 <- paste0("p = ", p_value(robust_model1.7$pval[2]))

sperm_plot = ggplot(sperm_data, aes(x = SCR.SCI, y = SMDH)) + 
              geom_violin(alpha = 0.1, aes(fill = SCR.SCI, colour = SCR.SCI)) + 
              geom_jitter(aes(x = SCR.SCI, y = SMDH, fill = SCR.SCI, colour = SCR.SCI, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.1) + 
              ylim(c(-1.5, 6))+
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Sperm Competition Intensity", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              #scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 2, 1)), y = 6, 
                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 2, 1)), y = 5.7, 
                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.7_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
                            show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.7_PI, aes(x = moderator, y = Est, colour= moderator), size = 5) +
              geom_segment(aes(x = 1, y = 5.3, xend = 2, yend = 5.3), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 3) + 
    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 3)

sperm_plot

```
# References
